\documentclass[11pt]{article} \input{preamble.tex} 
\usepackage{color}
\usepackage{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}

\newtheorem{proposition}[theorem]{Proposition}

\newcommand{\naturals}{\mathbb{N}}
\newcommand{\red}{\color{red}}
\newcommand{\blue}{\color{blue}}



\begin{document}
\handout{Class-info}{\today}{}{Lecturer: Peter Shor}{Class Information}{{\bf
18.345}}
\normalfont

\paragraph{Staff.} The lectures will be given by Peter Shor. There is also a
graduate TA, Ryuji Takagi, and another instructor, Ike Chuang, who will be
helping convert this class to Ed-X.  Contact information and office hours for us 
will be posted on the Stellar homepage. 

\paragraph{Grading.} The grade will be made up of weekly
problem set assignments
(xx\%), one in-class test (xx\%), and one final exam (xx\%). 
The in-class test will be held on October 26.
The final will be held during finals week.

\paragraph{Late Policy.} Problem sets will due online at 7pm.
It is possible to hand in a problem set late, with a 10\% decrease 
in your grade, until 7pm on the following day. 
We will not accept assignments turned in after the 
solutions are posted without a note from S$^3$.

\paragraph{Collaboration Policy.} Collaboration on homework is permitted, 
you should first think about the problems on your own. 
You must list the names of your collaborators on your submitted homework, 
or state that you had none. 

\paragraph{Student Support Services.} If you are dealing with a 
personal or medical issue that is impacting your ability to attend 
class, complete work, or take one of the exams, please discuss this 
with Student Support Services (S$^3$). The deans in S$^3$ will 
verify your situation, and then discuss with you how to address the
missed work. Students will not be excused from coursework or be 
given credit for homework more than one day late without verification 
from Student Support Services. You may consult with S$^3$  in 5-104 or 
at 617-253-4861. Also, S$^3$ has walk-in hours Monday-Friday 9:00--10:00am.



\end{document}

